RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-09-02 main.tex
:pencil: Update problem description

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

@@

		\emph{Third,} we consider an application scenario where multiple RIScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
		To investigate how RIScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
		This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.

@@

\begin{section}{Scattering Principles}
	Scattering refers to a change of moving direction of particles after colliding with others.
	It often involves \emph{diffuse reflection} where an incident ray is redistributed at many angles.
	An electromagnetic wave is scattered when an obstruction is placed in its propagation path.
	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.
	\begin{subsection}{Scatterer Categories}
		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
		\begin{subsubsection}{Antenna-Based Scatterer}
			A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
			It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
			According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
			For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
			At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
			The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
				\label{eq:reflection_pattern_antenna}
			\end{equation}
			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
		\end{subsubsection}
		\begin{subsubsection}{Metamaterial-Based Scatterer}
			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
				\label{eq:reflection_pattern_metamaterial}
			\end{equation}
			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
		\end{subsubsection}
	\end{subsection}

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by
		% \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
			\label{eq:passive_beamforming}
		\end{equation}
		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.
	\end{subsection}

@@

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
	In particular, passive RIScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:riscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

@@

@@

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
	\end{subsection}
	\label{se:riscatter}
\end{section}

\begin{section}{Rate-Region Characterization}
	To characterize the achievable primary-total-backscatter rate region of the proposed RIScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
	\end{maxi!}
	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

@@

		\begin{remark}
			In terms of total backscatter rate, the dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $\{x_{m_{\mathcal{K}}}\}$.
			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
			\label{re:augmented_source}
		\end{remark}

@@

		\begin{subsubsection}{Input Distribution}
			We compare the following input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Exhaustion:} Exhaustive grid search over the probability $K$-simplex with resolution $\Delta p = \num{1e-3}$;
				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};
				\item \emph{Cooperation:} Numerical symbol tuple distribution (i.e., $K$-dimensional joint probability array) evaluation by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a}.
			\end{itemize}

>>>>

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

@@

		\emph{Third,} we consider an application scenario where multiple RIScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
		To investigate how RIScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
		This is the first paper to reveal the importance of those factors in joint \gls{ris} and \gls{bc}/\gls{sr} design.

@@

\begin{section}{Scattering Principles}
	Scattering refers to a change of moving direction of particles after colliding with others.
	An electromagnetic wave is scattered to many angles when an obstruction is placed in its propagation path.
	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.
	\begin{subsection}{Scatterer Categories}
		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
		\begin{subsubsection}{Antenna-Based Scatterer}
			A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
			It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
			According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
			For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
			At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
			The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
				\label{eq:reflection_pattern_antenna}
			\end{equation}
			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
		\end{subsubsection}
		\begin{subsubsection}{Metamaterial-Based Scatterer}
			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
				\label{eq:reflection_pattern_metamaterial}
			\end{equation}
			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
		\end{subsubsection}
	\end{subsection}

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by
		% \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
			\label{eq:passive_beamforming}
		\end{equation}
		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio of state $m$.
		Lossless \gls{ris} assumes $\beta_m=1$ to maximize the available scattering power.
	\end{subsection}

@@

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of input distribution.
	In particular, the potentially dispersed passive RIScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:riscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

@@

		\label{se:system_model}

@@

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
		\label{se:information_theory}
	\end{subsection}
	\label{se:riscatter}
\end{section}

\begin{section}{Rate-Region Characterization}
	We notice the primary ergodic mutual information \eqref{eq:primary_mutual_information} relates to input distribution and active beamforming, while the total backscatter mutual information \eqref{eq:backscatter_mutual_information} depends explicitly on input distribution and implicitly on active beamforming and decision thresholds via backscatter \gls{dmtmac} \eqref{eq:dmtmac}.
	To characterize the achievable primary-total-backscatter rate region of the proposed RIScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
	\end{maxi!}

	Problem \eqref{op:weighted_sum_rate} introduces adaptive backscatter channel coding over conventional \gls{bc}/\gls{sr} designs.
	% Problem \eqref{op:weighted_sum_rate} generalizes conventional \gls{bc}/\gls{sr} by allowing adaptive backscatter channel coding.
	On the other hand, it also generalizes the discrete \gls{ris} phase shift selection problem by relaxing the feasible domain from the vertices of $M$-dimensional probability simplex to the simplex itself.
	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

@@

		\begin{remark}
			In terms of total backscatter rate, the potentially dispersed nodes with given input distribution can be viewed as an equivalent source with augmented alphabet of backscatter symbol tuples $\{x_{m_{\mathcal{K}}}\}$.
			As such, the \gls{dmtmac} \eqref{eq:dmtmac} is essentially a \gls{dmtc}, and problem \eqref{op:decision_threshold} reduces to the rate-optimal quantization design for a discrete-input continuous-output memoryless channel.
			\label{re:augmented_source}
		\end{remark}

@@

		\begin{subsubsection}{Input Distribution}
			We compare the following input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Exhaustion:} Exhaustive grid search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{1e-3}$;
				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};
				\item \emph{Cooperation:} Numerical symbol tuple distribution (i.e., $K$-dimensional joint probability array) evaluation by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a}.
			\end{itemize}
